Novel crystallization pathway\\and formation of ``colloidal rain'' during viscoelastic phase separation

### 2015-09-23 crystal_gel_letter.tex
insert fig:characterisation

\begin{figure}[!t]
 \centering
 \includegraphics[width=8cm]{oldfig/fig3a}
 \includegraphics[width=8cm]{oldfig/fig3d}
 % crystal_size.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=(atend)
 \caption{{\bf Characterisation of the crystal-gel.} {\bf a,} Time evolution of the average size of the crystals (black line) and the number of crystals (red line) for the state point $\phi=0.25$ and $c_p=0.38$. {\bf d,} Radius of gyration of crystalline nuclei at the late stages of gelation for the same state point.} 
 \label{fig:crystals}
\end{figure}

>>>>

\begin{figure}[!t]
 \centering
 \includegraphics{fig/characterisation.pdf}
 \caption{{\bf Characterisation of the crystal-gel.} {\bf a,} Time evolution of the average size of the crystals (blue line) and the number of crystals (red line) for the state point $\phi=0.25$ and $c_p=0.38$. {\bf d,} Radius of gyration of crystalline nuclei at the late stages of gelation for the same state point.} 
 \label{fig:crystals}
\end{figure}
